Registration timing

### 2023-09-21 notebook/analysis-issue.qmd
Move prop_to_provinces to a target
It was getting repetitive

# Load targets
tar_load(ongo)
tar_load(c(m_full_ordbeta, preds_issue, epreds_issue, issue_indicator_lookup))
invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
set_annotation_fonts()

prop_to_provinces <- function(x, lower = 1, upper = 32) {
  (x * (upper - lower)) + lower
}
```

>>>>

# Load targets
tar_load(ongo)
tar_load(c(m_full_ordbeta, preds_issue, epreds_issue, issue_indicator_lookup))
invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
set_annotation_fonts()
```

### 2023-09-21 notebook/analysis-local.qmd
Move prop_to_provinces to a target
It was getting repetitive

# Load targets
tar_load(ongo)
tar_load(c(m_full_ordbeta, preds_local, epreds_local))
invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
set_annotation_fonts()

prop_to_provinces <- function(x, lower = 1, upper = 32) {
  (x * (upper - lower)) + lower
}
```

>>>>

# Load targets
tar_load(ongo)
tar_load(c(m_full_ordbeta, preds_local, epreds_local))
invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
set_annotation_fonts()
```

### 2023-09-21 notebook/analysis-timing.qmd
Move prop_to_provinces to a target
It was getting repetitive

# Load targets
tar_load(ongo)
tar_load(c(m_full_ordbeta, preds_timing))
invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
set_annotation_fonts()

prop_to_provinces <- function(x, lower = 1, upper = 32) {
  (x * (upper - lower)) + lower
}
```

>>>>

# Load targets
tar_load(ongo)
tar_load(c(m_full_ordbeta, preds_timing))
invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
set_annotation_fonts()
```
